01-training and testing data

### 2019-03-06 journals/01-training_and_testing_data/01-training_and_testing_data.Rmd
work during meeting and presentation moved

>>>>

It is possible that the labels that Eric was using are different from the labels in my training dataset. In order to check whether I removed the correct datapoints, Heike suggested that I look at a parallel coordinate plots to see if the observations that were removed stand out as being unusual compared to the rest of the data. The code below prepares the training data before observations were removed to be plotted.

```{r}
# Create dataset for creating the paralle coordinate plot
par_data <- hamby173and252_train_cleaning %>%
  mutate(bbl1 = barrel1:bullet1:land1,
         bbl2 = barrel2:bullet2:land2) %>%
  mutate(category = factor(ifelse(!(bbl1 %in% c("6:2:1", "9:2:4", "Unknown:B:2",
                                                "Unknown:Q:4") | 
                                      bbl2 %in% c("6:2:1", "9:2:4", "Unknown:B:2",
                                                  "Unknown:Q:4")),
                           "keep", "remove"))) %>%
  arrange(category) %>%
  mutate(samesource_colors = ifelse(samesource == TRUE, rgb(1, 0, 0, alpha = 0.05), 
                                    rgb(0, 0, 0, alpha = 0.001)),
         samesource_colors2 = ifelse(samesource == TRUE, rgb(1, 0, 0, alpha = 0.001), 
                                    rgb(0, 0, 0, alpha = 0.01)),
         tankrash_colors = ifelse(category == "keep", rgb(0, 0, 1, alpha = 0.05),
                                  rgb(0, 0, 0, alpha = 0.01)))
```

The first plot shows the observations that were kept in black and the observations that were removed in blue. These observations do not stand out to me. It is not clear if these were the ones that were suppose to be removed or not. The second plot shows the observations from matches plotted in red, and the third plot shows the observations from nonmatches plotted in black.

```{r}
MASS::parcoord(par_data %>% select(ccf:sum_peaks), col = par_data$tankrash_colors)
MASS::parcoord(par_data %>% select(ccf:sum_peaks), col = par_data$samesource_colors)
MASS::parcoord(par_data %>% select(ccf:sum_peaks), col = par_data$samesource_colors2)
```
